{\fontfamily{ptm}\selectfont A Proximal Point framework of Nesterov type accelerated gradient}

### 2024-08-07 Notebook LaTEX/Momentum Accelerations/main.tex
>w<, work over, work home sync

    \par\noindent
    \textbf{We state our contributions}. 
    In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
    We stated different forms of accelerated gradient that appeared in the literatures and the equivalences between their forms. 
    They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
    Abstract forms related to the proximal gradient method were our own inventions inspired by discussions in the literatures, which includes 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
    \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}. 
    In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
    we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind. 
    In
    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
    This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper. 
    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
    In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.

@@

            \begin{definition}[AG Proximal Gradient Generic Form]
            \label{def:ag_prox_grad_tri_pt}
                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
                Define proximal gradient and gradient mapping operator 
                $$
                \begin{aligned}
                    \mathcal T_L(x) 
                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
                    \\
                    x^+ &= \mathcal T_L(x), 
                    \\
                    \mathcal G_L(x) 
                    &:= L(x -  x^+). 
                \end{aligned}
                $$
                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
                $$
                \begin{aligned}
                    y_t^+ &= \mathcal T_L(y_t)
                    \\
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \end{aligned}
                $$
                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
            \end{definition}
            \begin{remark}
                Observe that $z_{t + 1} = y_t^+$. 
            \end{remark}

@@

            \begin{definition}[Proximal Gradient variant of Ryu 12.1]
            \label{def:ag_tri_pt_form_E}
                The method appeared in Ryu's text is a special case of 
                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
                \begin{align*}
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
                \end{align*}
            \end{definition}

            \begin{definition}[Similar Triangle Form I]
            \label{def:ag_form_similar_tria_I}
                The similar triangle form is equivalent to the classic nesterov accelerated gradient proposed back in 1983. 
                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
                \begin{align*}
                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
                    \\
                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (x_{t + 1} + L\eta_{t + 1}z_{t + 1}). 
                \end{align*}
            \end{definition}
            \begin{observation}
                There are a lot of observations about this form to unpack. 
                Let's list the following observations
                \begin{enumerate}
                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$. Hence $z_t, y_t, x_t$ are three collinear points. Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \mathcal G_L(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \mathcal G_L(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$. 
                \end{enumerate}
                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
            \end{observation}
            \begin{remark}
                The above algorithm is a special case of 
                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}, 
                see 
                \hyperref[sec:scenario_ii]{section \ref*{sec:scenario_ii}} for more information. 
            \end{remark}

@@

                \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}

@@

        \begin{theorem}[Generic AG Convergence]
        \label{thm:generic_ag_convergence}
            If there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
            \begin{align*}
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)
                \Upsilon_{2, t + 1}^{\text{AG}} + 
                \Upsilon_{1, t + 1}^{\text{AG}} 
                &\le \delta_{t + 1} \quad 
                \forall t \in \mathbb N, 
                \\
                \Upsilon_{1, 1}^{\text{AG}} &\le \delta_1. 
            \end{align*}
            then with 
            \begin{align*}
                S_t &:= \sum_{i = 1}^{t} \delta_i
                \\
                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
                \\
                \Phi_t &= \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
                \\
                \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
            \end{align*}
            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, which allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$. 
        \end{theorem}
        \begin{proof}
            By definition we have
            {\footnotesize
            \begin{align*}
                \Phi_{t + 1} - \Phi_t 
                &= 
                \left(
                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
                \right) (f(z_{t + 1}) - f(x_*)) 
                - 
                \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_{t}) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= 
                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
                +
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)(f(z_{t + 1}) - f(z_t))
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
            \end{align*}
            }
            Telescoping we have 
            \begin{align*}
                \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
                \\
                \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
                \\
                \Phi_T - \Phi_0 &\le 
                \sum_{i = 1}^{T}\delta_i = S_{T}. 
            \end{align*}
            So then $\Phi_T - \Phi_0$ yields: 
            $$
            \begin{aligned}
                \sigma_T (f(z_t) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2 
                - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
                &\le S_{T}
                \\
                \implies 
                \sigma_T(f(z_t) - f(x_*))
                &\le 
                S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
                \\
                f(z_t) - f(x_*) &\le 
                \sigma_T^{-1}\left(
                    S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
                \right),
            \end{aligned}
            $$
            which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
            When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
        \end{proof}

        \begin{theorem}[Constraints on the PPM stepsize sequence]
            \;\\
            Algorithm proposed back in 
            \hyperref[def:ag_prox_grad_tri_pt]{definition \ref*{def:ag_prox_grad_tri_pt}}
            converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
            \begin{align*}
                \begin{cases}
                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
                    = 
                    \epsilon_{t + 1} \tilde \eta_{t + 1}
                    & \forall t \in \mathbb N, 
                    \\
                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
                    & \forall t \in \mathbb N. 
                \end{cases}
            \end{align*}
            Here $\epsilon_{t + 1}$ is an arbitrary sequence made represent the quantity in the left hand side. 
            Then such a sequence creates 
            \begin{align*}
                \Phi_{t + 1} - \Phi_t =
                \Upsilon_{1, t + 1}^\text{AG} + 
                \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}
            \end{align*}

        \end{theorem}
        \begin{proof}

>>>>

    \par\noindent
    \textbf{We state our contributions}. 
    In \hyperref[sec:AG_varieties]{section \ref*{sec:AG_varieties}} 
    We stated different forms of accelerated gradient that appeared in the literatures and the equivalences between their forms. 
    They are abstract because the choice of stepsize parameters in the algorithms are unspecified. 
    Abstract forms related to the proximal gradient method were our own inventions inspired by discussions in the literatures, which includes 
    \hyperref[def:ag_prox_grad_ppm]{definition \ref*{def:ag_prox_grad_ppm}}, and 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    In \hyperref[sec:AG_useful_information]{section \ref*{sec:AG_useful_information}}
    we prove and interpret some of the unproved claims made by Ahn, Sra \cite{ahn_understanding_2022} as good exercises and for the peace of the mind. 
    In
    \hyperref[sec:generic_ag_ppm_lyapunov_analysis]{section \ref*{sec:generic_ag_ppm_lyapunov_analysis}},
    we state two important theorems for the derivation of convergences rate for various type of algorithm using an upper bound of a Lyapunov function. 
    This part is inspired by works from Ahn, Sra \cite{ahn_understanding_2022}, but with the gradient mapping and proximal gradient added into the picture, making it distinct from all algorithms discussed in Ahn and Sra's paper. 
    \hyperref[sec:scenario_i]{Section \ref*{sec:scenario_i}} and 
    \hyperref[sec:scenario_ii]{\ref*{sec:scenario_ii}} derive the convergence rate and determine the parameters for the step sizes needed to achieve an optimal convergence rate. 
    In each section, we recover a specific variant of the Accelerated gradient and identify their appearances in the literature.

@@

            \begin{definition}[AG Proximal Gradient Generic Form]
            \label{def:ag_prox_grad_generic}
                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
                Define proximal gradient and gradient mapping operator 
                $$
                \begin{aligned}
                    \mathcal T_L(x) 
                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
                    \\
                    x^+ &= \mathcal T_L(x), 
                    \\
                    \mathcal G_L(x) 
                    &:= L(x -  x^+). 
                \end{aligned}
                $$
                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
                $$
                \begin{aligned}
                    y_t^+ &= \mathcal T_L(y_t)
                    \\
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \end{aligned}
                $$
                for all $t\in \mathbb N$ where the base case has $y_0 = x_0$. 
            \end{definition}
            \begin{remark}
                Observe that $z_{t + 1} = y_t^+$. 
            \end{remark}

@@

            \begin{definition}[Proximal Gradient variant of Ryu 12.1]
            \label{def:ag_tri_pt_form_E}
                The method appeared in Ryu's text is a special case of 
                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
                with the condition that $\tilde \eta_t = \eta_t$ for all $t \in \mathbb N$ and $g \equiv 0$ for the non-smooth part of the objective. 
                As a consequence, the algorithm has the following updates for iterates $(y_t, x_{t + 1}, z_{t + 1})$: 
                \begin{align*}
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \eta_t \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t).
                \end{align*}
            \end{definition}

            \begin{definition}[Similar Triangle Form I]
            \label{def:ag_form_similar_tria_I}
                The similar triangle form is equivalent to the classic nesterov accelerated gradient proposed back in 1983. 
                It updates iterates $(y_t, x_{t + 1}, z_{t + 1})$ using 
                \begin{align*}
                    z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t) 
                    \\
                    x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (x_{t + 1} + L\eta_{t + 1}z_{t + 1}). 
                \end{align*}
            \end{definition}
            \begin{observation}
                There are a lot of observations about this form to unpack. 
                Let's list the following observations
                \begin{enumerate}
                    \item Observe that $y_t = (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)$ is a convex combination between $x_t, z_t$. Hence $z_t, y_t, x_t$ are three collinear points. Additionally, we have $y_t - x_t = L\eta_t (z_t - y_t)$, hence $\Vert y_t - x_t\Vert/\Vert z_t - y_t\Vert = L\eta_t$. 
                    \item By the algorithm, we have $z_{t + 1} - y_t = - L^{-1} \mathcal G_L(y_t)$, and $x_{t + 1} - x_t = - \tilde \eta_{t + 1} \mathcal G_L(y_t)$, hence vector $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
                    \item Finally, with update $x_{t +1} - z_{t + 1} = L\eta_t (z_{t +1} - z_t)$, we have three colinear points $(z_t, z_{t + 1}, x_t)$ with $\Vert z_{t + 1} - z_t\Vert/\Vert z_{t +1 } - z_t\Vert = L\eta_t$. 
                \end{enumerate}
                From the above results, we can conclude that triangle $(y_t, z_t, z_{t + 1})$ is similar to $(x_t, z_t, x_{t + 1})$ because they share colinear points $z_t, y_t, x_t$ and $z_t, z_{t + 1}, x_{t + 1}$, and their sides $z_{t + 1} - y_t$ parallels to $x_{t + 1} - x_t$. 
            \end{observation}
            \begin{remark}
                The above algorithm is a special case of 
                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
                see 
                \hyperref[thm:ag_generic_stepsize_constrants]{section \ref*{thm:ag_generic_stepsize_constrants}} 
                for more information. 
            \end{remark}

@@

                \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}

@@

        \begin{theorem}[Generic AG Convergence]
        \label{thm:generic_ag_convergence}
            Define the Lyapunov function $\Phi_t\; \forall t \in \{0\}\cup \N$: 
            \begin{align*}
                \Phi_t &= \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_t) - f(x_*)) + \frac{1}{2}\Vert x_t - x_*\Vert^2 \quad \forall t \in \NN
                \\
                \Phi_0 &= \frac{1}{2}\Vert x_0 - x_*\Vert^2, 
            \end{align*}
            if there is a choice of $\eta_i, \tilde \eta_i$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} such that we have 
            \begin{align*}
                & \Phi_{t + 1} - \Phi_{t}\left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right) =
                \Upsilon_{2, t + 1}^{\text{AG}} + 
                \Upsilon_{1, t + 1}^{\text{AG}} 
                \le \delta_{t + 1} \quad 
                \forall t \in \mathbb N, 
                \\
                & \Upsilon_{1, 1}^{\text{AG}} \le \delta_1. 
            \end{align*}
            Then with
            \begin{align*}
                S_t &:= \sum_{i = 1}^{t} \delta_i
                \\
                \sigma_t &:= \sum_{i = 1}^{t}\tilde \eta_i
            \end{align*}
            we have $\Phi_{t + 1} - \Phi_t \le \delta_{t + 1}$, it allows for a convergence rate of $\mathcal O \left(\sigma_T^{-1}S_T\right)$ of $f(z_T) - f(x_*)$ when $S_T \neq 0$ and a rate of $\mathcal O(\sigma_T^{-1})$ when $S_T = 0$. 
        \end{theorem}
        \begin{proof}
            By definition we have
            {\footnotesize
            \begin{align*}
                \Phi_{t + 1} - \Phi_t 
                &= 
                \left(
                    \sum_{i = 1}^{t+1} \tilde\eta_{i}
                \right) (f(z_{t + 1}) - f(x_*)) 
                - 
                \left(
                    \sum_{i = 1}^{t} \tilde\eta_{i}
                \right) (f(z_{t}) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= 
                \tilde \eta_{t + 1} (f(z_{t + 1}) - f(z_*))
                +
                \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)(f(z_{t + 1}) - f(z_t))
                + \frac{1}{2}\Vert x_t - x_*\Vert^2
                - \frac{1}{2}\Vert x_{t + 1} - x_*\Vert^2
                \\
                &= \left(
                    \sum_{i = 1}^{t} \tilde \eta_i
                \right)\Upsilon_{2, t + 1}^{\text{AG}} + \Upsilon_{1, t + 1}^{\text{AG}} \le \delta_{t + 1}. 
            \end{align*}
            }
            Telescoping we have 
            \begin{align*}
                \Phi_{t + 1} - \Phi_t &\le \delta_{t + 1}
                \\
                \sum_{i = 0}^{T - 1}\Phi_{i + 1} - \Phi_i &\le \sum_{i = 0}^{T - 1}\delta_{i + 1}
                \\
                \Phi_T - \Phi_0 &\le 
                \sum_{i = 1}^{T}\delta_i = S_{T}. 
            \end{align*}
            So then $\Phi_T - \Phi_0$ yields: 
            $$
            \begin{aligned}
                \sigma_T (f(z_t) - f(x_*)) 
                + \frac{1}{2}\Vert x_t - x_*\Vert^2 
                - \frac{1}{2}\Vert x_0 - x_*\Vert^2 
                &\le S_{T}
                \\
                \implies 
                \sigma_T(f(z_t) - f(x_*))
                &\le 
                S_T + \frac{1}{2}\Vert x_0 - x_*\Vert^2
                \\
                f(z_t) - f(x_*) &\le 
                \sigma_T^{-1}\left(
                    S_{T} + \frac{1}{2}\Vert x_0 - x_*\Vert^2
                \right),
            \end{aligned}
            $$
            which yields a convergence rate $\mathcal O(\sigma_T^{-1}S_{T})$. 
            When $S_T = 0$, the convergence rate is $O(\sigma_T^{-1})$ instead. 
        \end{proof}

        \begin{theorem}[Constraints on the PPM stepsize sequence]
            \label{thm:ag_generic_stepsize_constrants}
            \;\\
            Algorithm formulated in 
            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
            converges if the stepsize sequence $\eta_i, \tilde \eta_{i}$ satisfies
            \begin{align*}
                \begin{cases}
                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
                    = 
                    \epsilon_{t + 1} \tilde \eta_{t + 1}
                    & \forall t \in \mathbb N, 
                    \\
                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
                    & \forall t \in \mathbb N. 
                \end{cases}
            \end{align*}
            Here $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$ is a sequence made characterizing the error between $\tilde \eta_{t + 1}, \eta_t - L^{-1}$. 
            Then the convergence rate can be formulated by
            \begin{align*}
                \Phi_{t + 1} - \Phi_t =
                \Upsilon_{1, t + 1}^\text{AG} + 
                \sigma_t\Upsilon_{1, t + 1}^{\text{AG}} 
                &\le \epsilon_{t + 1}\tilde\eta_{t + 1} \Vert \mathcal G_L(y_t)\Vert^2 \le \delta_{t + 1}.
            \end{align*}
            When $\eta_t - 0 \;\forall t\in \mathbb N$, the sequence $a_t:= a_t = 1 + L \eta_t = \tilde \eta_{t + 1} - \epsilon_{t + 1}$, the relation simplies to: 
            \begin{align*}
                \begin{cases}
                    a_{t + 1} &= (1/2)\left(
                    1 + \sqrt{1 + 4 c_{t + 1}}
                    \right), 
                    \\
                    c_{t + 1} &= a_t^2.     
                \end{cases}
            \end{align*}
            As a consequence: 
            \begin{enumerate}
                \item It makes $\delta_{t} = 0$ in the Lypunov analysis; 
                \item it simplifies the algorithm to
                \hyperref[def:ag_form_similar_tria_I]{definition\ref*{def:ag_form_similar_tria_I}}; 
                \item and it is the famous Nesterov momentum sequence. 
            \end{enumerate}
            With $t \in \mathbb N \cup \{0\}$ fixed, 
            recall that for the proximal gradient PPM generic form 
            (as formulated in 
            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}
            ) for $t\in \mathbb N$ it has: 
                y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t). 
            Recall the upper bounds from 
            \ref*{thm:generic_ag_convergence}, 
            it has 
            By the updates, vector $x_{t + 1} - x_t$ and $z_{t + 1} - y_t$ are parallel by observations: 
                x_{t + 1} - x_t &= -\tilde\eta_{t + 1}\mathcal G_L(y_t), 
                z_{t + 1} - y_t &= -L^{-1}\mathcal G_L(y_t). 
            This allows for 
                \Upsilon_{1, t + 1}^{\text{AG}} 
                - \frac{1}{2}\Vert x_{t + 1} - x_t\Vert^2 + 
                \frac{\tilde\eta_{t + 1}L}{2}\Vert z_{t + 1} - y_t\Vert^2 
                \langle \tilde\eta_{t + 1}\mathcal G_L (y_t), x_{t + 1} - z_{t + 1} \rangle
                - \frac{1}{2}\Vert \tilde\eta_{t + 1} \mathcal G_L\Vert^2 + 
                \frac{\tilde\eta_{t + 1}L}{2}\Vert L^{-1} \mathcal G_L(y_t)\Vert^2
                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), x_{t + 1} - z_{t + 1} \rangle
                \frac{1}{2}\left(
                    - \tilde\eta_{t + 1}^2 + 
                    L^{-1}\tilde\eta_{t + 1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    (x_{t + 1} - x_{t}) + x_t
                    + (y_t - z_{t + 1}) - y_t
                \frac{1}{2}\left(
                    L^{-1}\tilde\eta_{t + 1}
                    - \tilde\eta_{t + 1}^2
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    -\tilde\eta_{t + 1}\mathcal G_L(y_t) + x_t 
                    + L^{-1}\mathcal G_L(y_t) - y_t
                \frac{1}{2}\left(
                    L^{-1}\tilde\eta_{t + 1}
                    - \tilde\eta_{t + 1}^2
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    \tilde\eta_{t +1}\mathcal G_L(y_t), 
                    (L^{-1} - \tilde\eta_{t + 1})\mathcal G_L(y_t) + x_t - y_t
                &= \frac{1}{2}\left(
                    L^{-1}\tilde\eta_{t + 1} - \tilde\eta_{t + 1}^2 
                    + 2 \tilde\eta_{t + 1}^2 - 2\tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2
                    x_t - y_t
                \frac{1}{2}\left(
                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2 
                + \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), y_t - x_t\rangle.
            Similarly 
                \Upsilon_{2, t + 1}^{\text{AG}} 
                \langle \mathcal G_L(y_t), z_{t + 1} - y_t + y_t - z_t\rangle
                + \frac{L}{2}\Vert z_{t + 1} - y_t\Vert^2
                \langle \mathcal G_L(y_t), - L^{-1} \mathcal G_L(y_t) + y_t - z_t\rangle
                \frac{L}{2}\Vert L^{-1}\mathcal G_L(y_t)\Vert^2
                -L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
                (1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2 
                \langle \mathcal G_L(y_t), y_t - z_t\rangle
                -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
                \langle \mathcal G_L(y_t), y_t - z_t\rangle. 
            Observe that the cross product term for $\Upsilon_{1, t + 1}^\text{AG}, \Upsilon_{2, t + 1}^\text{AG}$ doesn't match. 
            Hence let's consider the update for $y_t$, which can be written as $y_t - x_t = L \eta_t (z_t - y_t)$. We make the choice to do surgery on upper bound of $\Upsilon_{2, t + 1}^\text{AG}$, so $\langle \mathcal G_L(y_t), y_t - x_t\rangle = \langle \mathcal G_L(y_t), L \eta_t (z_t - y_t)\rangle$. 
            With this in mind, RHS of $\phi_{t + 1} - \phi_t$ yields: 
                &\Upsilon_{1, t + 1}^\text{AG} + 
                    \sum_{i = 1}^{t}\tilde\eta_i 
                \right)\Upsilon_{1, t + 1}^{\text{AG}}
                \frac{1}{2}\left(
                    \tilde\eta_{t + 1}^2 - \tilde\eta_{t + 1}L^{-1}
                \right)\Vert \mathcal G_L(y_t)\Vert^2 
                \langle \tilde\eta_{t + 1} \mathcal G_L(y_t), L\eta_t(z_t - y_t)\rangle
                    \sum_{i = 1}^{t}\tilde\eta_i 
                \right)\left(
                    -(1/2)L^{-1}\Vert \mathcal G_L(y_t)\Vert^2
                    \langle \mathcal G_L(y_t), y_t - z_t\rangle
                    \frac{1}{2}\tilde\eta_{t + 1}\left(
                        \tilde \eta_{t +1} - L^{-1}
                    \frac{1}{2L}\sum_{i = 1}^{t}\tilde \eta_i
                \right)\Vert \mathcal G_L(y_t)\Vert^2 + 
                    L\eta_t \tilde \eta_{t + 1} - \sum_{i = 1}^{t}\tilde \eta_i
                \right)\langle \mathcal G_L(y_t), z_t - y_t\rangle. 
            The non-negativity of $\Vert \mathcal G_L(y_t) \Vert^2$ characterize the culmulative error $\delta_{t + 1}$ in the Lypunov analysis through sequence $\epsilon_i$. 
            Setting the coefficient of $\Vert \mathcal G_L(y_t) \Vert^2$ to be $\epsilon_{t + 1}\tilde \eta_{t + 1}$, it yields a system of inequality: 
                \begin{cases}
                    \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
                    - L^{-1} \sum_{i= 1}^{t}\tilde \eta_i 
                    = 
                    \epsilon_{t + 1} \tilde \eta_{t + 1}
                    & \forall t \in \N, 
                    L \eta_t \tilde \eta_{t + 1} = \sum_{i=1}^{t}\tilde \eta_i 
                    & \forall t \in \N. 
                \end{cases}
            It requires base case $L\eta_0\tilde\eta_{1} = 0$, assume $\sigma_0 = 0$. 
            We use $\sum_{i = 1}^t \tilde \eta_i = \sigma_t$, simplifying the first equation we have 
                \tilde \eta_{t + 1} (\tilde \eta_{t + 1} - L^{-1})
                - L^{-1} \sigma_t
                \epsilon_{t + 1} \tilde \eta_{t + 1}
                \tilde \eta_{t + 1} ^2 - L \tilde \eta_{t + 1} 
                \epsilon_{t + 1} \tilde \eta_{t + 1} + L^{-1} \sigma_t
                \epsilon_{t + 1} \tilde \eta_{t + 1} 
                + L^{-1}(L \eta_t \tilde \eta_{t + 1})
                \tilde \eta_{t + 1} &= \epsilon_{t + 1} + \eta_t + L^{-1}. 
            At the last step, we divided both side of the equation by $\tilde \eta_{t + 1} > 0$.
            The parameter gives relation $\epsilon_{t+1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$. 
            Hence, it gives us the following system of equality to work with 
                \forall t \in \N: 
                \begin{cases}
                    \tilde \eta_{t + 1} = \epsilon_{t + 1} + \eta_t + L^{-1}, 
                    L \eta_t \tilde \eta_{t + 1} = \sigma_t.     
                \end{cases}
            With that, we can solve a relation between $\eta_{t + 1}$ in terms of the sequence $\epsilon$ and $\eta_t$.
            Consider the equality

            \begin{align*}
                L \sigma_{t + 1} &= L \tilde \eta_{t + 1} + L \sigma_t
                \\
                &=
                L \tilde \eta_{t + 1}  + L (L \eta_t \tilde \eta_{t + 1})
                \\
                &= L \tilde \eta_{t+ 1} + L \eta_t (L \tilde \eta_{t + 1})
                \\
                &=  L \tilde \eta_{t+ 1} + L \eta_t (L \epsilon_{t + 1} + L \eta_t + 1)
                \\
                &=  L \tilde \eta_{t+ 1} + L \eta_t (L \eta_t + 1) + L^2 \eta_t \epsilon_{t + 1}
                \\
                &= L (\epsilon_{t +1} + \eta_t + L^{-1}) + L\eta_t(L \eta_t + 1) + L^2\eta_t \epsilon_{t + 1}
                \\
                &= L \epsilon_{t + 1} + (L\eta_t + 1)^2 + L^2\eta_t \epsilon_{t + 1}
                \\
                &= 
                L \epsilon_{t + 1}(1 + L \eta_t) + (1 + L \eta_t)^2. 
            \end{align*}

            At the same time we have

            \begin{align*}
                L \sigma_{t + 1} &= L^2 \eta_{t + 1}\tilde \eta_{t + 1} 
                \\
                &= L\eta_{t + 1}(1 + L \eta_{t + 1} + \epsilon_{t + 2})
                \\
                &= L\eta_{t + 1}(1 + L \eta_{t + 1}) + \epsilon_{t + 2}L\eta_{t + 1}. 
            \end{align*}

            Therefore, it generates the following equation:
